\section{Meetings for the project}



\begin{tcolorbox}[
	title=Meeting 1 - From Green FabLab to FabCity,
	breakable,
	toptitle=3mm,
	colback=blue!5!white,
	colframe=blue!75!black,
	colbacktitle=blue!30,
	coltitle=blue!20!black,  
	fonttitle=\bfseries,
	subtitle style={boxrule=0.4pt,
		colback=blue!50!yellow!5!white} ]



\begin{flushleft}
	\begin{tabular}{l l l l}
		
		{\Large \textbf{Date:}}	& October 16, 2017 & &\\
		{\Large \textbf{Reunion \#: }} & 1 & & \\ 
		{\Large \textbf{Place: }} & LF2L & &\\ % Partner names
		{\Large \textbf{Présents : }}	& \tabitem Laurent Dupont& \tabitem Fabio Cruz  & \\		
	\end{tabular}
\end{flushleft}


	\tcbsubtitle{Goal of the meeting FabCities}

	To establish a the first elements to consider for the project.

	\begin{itemize}
		\item Project framework
		\item Establishment of the firs elements to explore.
		\item Modalities for work.
		\item Project Success Factors for Stakeholders
	\end{itemize}

	\tcbsubtitle{Discussion/ Comments / Questions}

	Students group (\href{mailto:ensgsi.greenfabprojet@gmail.com}{ensgsi.greenfabprojet@gmail.com}) is composed by:
	\begin{enumerate}
		\item Betty (She is going to leave at end of January. She is going to be remplaced by another student coming from "double-diplome")
		\item Marie
		\item Robin 
		\item Quentin (06 08 86 02 86)
	\end{enumerate}


	\begin{itemize}
		\item First impression of the group.
		\item Working methods to be validated (notably uses of the LF2L, IBM platform to share and capitalize, etc.)
		\item Purpose of the project to be validated given the richness and complexity
		\item 
	\end{itemize}

Bibliography elements already given:

\begin{itemize}
	\item \href{http://www.newpic.fr/wbopenlabs/anrt-newpic-livreblancopenlabs-hd.pdf}{White book }			
	\item \fullcite{Niaros2016}
\end{itemize}


Documents to give if necessary:

\begin{itemize}
	\item Rapport du projet 2AI 2016-2017 : LF2L Territorial
\end{itemize}



\textbf{Definition of the }

	\begin{itemize}
		\item Benchmarking of the FabCity's projects and practices
			
			\begin{itemize}
				\item What?, Who?, Where?, How?
				\item Territorial diagnosis
				\item MRT				
			\end{itemize}
		
		\item Identification of the practices that are required to consider  in a FabCity status.

			\begin{itemize}
				\item What?, Who?, Where?, How?
				\item Size?
				\item Financial aspects
				\item Stakeholders
				\item Thematic	
				\item Approaches bottom-up / top-down / horizontal 
			
			\end{itemize}
		
		\item Is \textbf{Green Fablab} project a driver for a candidature for FabCity?
			\begin{itemize}
				\item Description of the concept and goals to meet.
				\item Stakeholders and resources to consider.
				\item Links to be made with other approaches already undertaken, eg: LF2L Territorial (project 2AI 2016-2017)
				\item Planning
			\end{itemize}
				
	\end{itemize}

	\tcbsubtitle{Driver sucess factors for the project}
		
For the students:
		\begin{itemize}
			\item 
		\end{itemize}

Fabio:
	\begin{itemize}
		\item Relationship betwen Green FabLab and FabCity.
		\item Identification of the different iniciatives of local recycling at the different Fabcities.
		\item Identification of possible recycling projects at the fablab scale.
		\item Establishment of the importance of the 3D printing for a FabCity concept.
	\end{itemize}

Hakim:
\begin{itemize}
	\item 
\end{itemize}

Mauricio:
\begin{itemize}
	\item 
\end{itemize}

Laurent D:
\begin{itemize}
	\item  Agreeable environment between students and tutors.
	\item Balanced consideration  between the \textbf{Fab} and \textbf{Living} concepts
	\item Conceptual illustration of the FabCity concept at the scale of the Quartier (around the LF2L), the Nancy Metropolis, Lorraine region, Grand Est region.
	
	\item Synergie with the 1AI project.
	\item Participation at the International fair 2018.

		\begin{itemize}
			\item Materialize 
			\item Users tests and feedback gained during the defense and the final report			
		\end{itemize}

	\item Creation of new partnership with others stakeholders?
	\item Scientific article?, research master?, Thesis?.
	
\end{itemize}




	\tcbsubtitle{Things to do for the next meeting}
	
	\begin{itemize}
		\item Meeting before Hakim and Fabio's depart to OctoberMake.
		\item Send working plan to the students
		\item Template of candidature for FabCity?
	\end{itemize}
	
	
	\tcbsubtitle{Date of the Next Meeting}
	
	\textcolor{blue}{\textbf{Friday 27/10, 2017 14h at LF2L}}
	
\end{tcolorbox}








